Viscous Erosion in Porous Media

### 2018-04-05 docs/methods/erosion_methods.tex
NM

Erosion is a fluid-mechanical process responsible for a variety
of phenomena in geophysical and other settings.  For example,
wind erosion causes sand dunes to be  longer on the windward
side~\cite{han1969}, while stream-bed erosion is responsible for branching structures
of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  Erosion is
also important in biophysical applications---plaque erosion in arteries
is key to understanding heart disease~\cite{sha2002,
gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can
be explained by erosion~\cite{pic-van-hei2000}. 
Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}. All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions} The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
In this fashion, individual pores are resolved rather than
homogenized.  A boundary integral equation (BIE) is used to solve the
incompressible Stokes equations in the complex geometry.  The resulting
method resolves individual grains and the non-negligible interactions
between bodies.  To link the eroding body and fluid dynamics, the body
is eroded in the normal direction at a rate that is proportional to the
magnitude of the shear stress.

>>>>

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), as well as biological structures like plaque and biofilms. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.

Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{}, as well as related processes such as dissolution \cite{} and melting \cite{}. In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
The example of an eroding porous medium presents new challenges and opportunities in that multiply connected domains must be considered. Furthermore, the long-range effects of Stokes flow facilitates even stronger coupling between bodies.

The example of an eroding porous medium presents new and interesting opportunities in a few ways. First of all, the medium is composed of many bodies and so multiply-connected domains most be considered. These bodies can interact via the surrounding flow. In particular, Stokes flow enables long-range interactions, which strongly couples the shape evolution of difference bodies.

%% ORIGINAL %%%
\vsp{5}
%sand dunes to be  longer on the windward side~\cite{han1969}, 
%stream-bed erosion is responsible for branching structures of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  
%Erosion is also important in biophysical applications---plaque erosion in arteries is key to understanding heart disease~\cite{sha2002, gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can be explained by erosion~\cite{pic-van-hei2000}.

Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.

All of these processes involve a feedback process between how boundaries move and how flow evolves and thus can be conceptually linked  as `sculpting with flow'~\cite{ristroph2018sculpting}.
% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.

@@

\vsp{5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions} The present study develops numerical methods
to simulate erosion of multiply-connected two-dimensional geometries.
In this fashion, individual pores are resolved rather than
homogenized.  A boundary integral equation (BIE) is used to solve the
incompressible Stokes equations in the complex geometry.  The resulting
method resolves individual grains and the non-negligible interactions
between bodies.  To link the eroding body and fluid dynamics, the body
is eroded in the normal direction at a rate that is proportional to the
magnitude of the shear stress.
